---
title: "emojidata package"
author: "Taikgun Song"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include=F}
library(emojidata)
```

# Data: emoji_v5.0

The data of the current package comes from [`Emoji List v5.0`](http://www.unicode.org/emoji/charts/emoji-list.html). The table from the web page is contained in `data(emojidata)`. The data set consist of the following information:

 * emoji number
 * emoji Unicode
 * emoji name
 * Three hierarchical categories of Emoji.
    cat1 being the largest, cat 2 is a sub category of cat1, and so on.
 * emoji keyword
 * emoji image in png

```{r, eval=F}
data("emojidata")
```


# Data: loec

loec stands for 'list of emoji categories'.
Not an official categories from the unicode.org, please use the `data(emojidata)` for the official categories. Categories in `data(loec)` was categorized by the author for his own research.


```{r, eval=F}
data("loec")
```
